Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}

### 2020-03-12 defesa/article/e3p.tex
wip

Initially, E3P is a problem with three unknown variables: $(q_x, q_y)$, and $\theta$. However, we can reduce this number to only one, as it will be shown, it is possible to obtain $q$ from $\theta$.
Let us assume that point $u$ is at the origin. If it is not, a simple translation by $-u$ applied to the three points can be made to put $u$ at the origin.
Assume as well that $(q, \theta)$ is a solution of E3P.

>>>>

Initially, E3P is a problem of determining the values of three unknown continuous variables $(q_x, q_y)$, and $\theta$. However, as it will be shown, we can reduce this number to only one, as it is possible to obtain $q$ uniquely from $\theta$.
Let us assume that point $u$ is at the origin. If it is not, a simple translation by $-u$ applied to the three points can be made to put $u$ at the origin.
Assume as well that $(q, \theta)$ is a solution of E3P.
